--- 
title: TidyTuesday Waste Water Treatment Plant Dataset EDA
year: 2022
week: 38
author: (@dorrajmachai)[https://github.com/dorrajmachai]
---

# TidyTuesday 2022 - Week 38

This week's TidyTuesday challenge deals with wastewater treatment plants! To begin, let's load our libraries and our data:


```{r}

library("lubridate")
library("tidyverse")

tuesdata <- tidytuesdayR::tt_load(2022, week = 38)
HydroWASTE_v10 <- tuesdata$HydroWASTE_v10
```

Okay, now we can take a look at our data and begin our analysis!

```{r}

HydroWASTE_v10 # I am giving this a different title
dataset <- HydroWASTE_v10

glimpse(dataset)
colnames(dataset)
```

So, that's our data! I'm not familiar with this topic and even more unfamiliar with its specifics in this part of the world. The discussion is linked on the TidyTuesday github page.

```{r}


renamed_set <- dataset %>%
	rename(
		   wasteid = WASTE_ID,
		   source = SOURCE, 
		   id = ORG_ID,
		   name = WWTP_NAME,
		   country = COUNTRY,
		   country_iso = CNTRY_ISO,
		   location_lat = LAT_WWTP,
		   location_lon = LON_WWTP,
		   quality_indicator = QUAL_LOC,
		   latitude_out = LAT_OUT,
		   longitude_out = LON_OUT,
		   status = STATUS,
		   populationserved = POP_SERVED,
		   quality_population = QUAL_POP,
		   discharged = WASTE_DIS,
		   quality_discharged = QUAL_WASTE,
		   level = LEVEL,
		   quality_level = QUAL_LEVEL,
		   df = DF,
		   riverreach_id = HYRIV_ID,
		   river_discharge = RIVER_DIS,
		   tenkilo_outfall = COAST_10KM,
		   fiftykilo_outfall = COAST_50KM,
		   designcapacity = DESIGN_CAP,
		   capacity_quality = QUAL_CAP
	)
```

```{r}

colnames(renamed_set)
```

After renaming the columns in our dataset, we can take a look at all of the variables:

```{r}

renamed_set["country"] %>%
	distinct() %>%
	print(n = 188)
```

```{r}

library(ggthemes)

renamed_set %>%
	group_by(quality_indicator) %>%
	ggplot(aes(location_lon, location_lat)) +
	geom_point(color = renamed_set$quality_indicator, 
			   size = 0.5) +
	borders("world") +
	theme_map() +
	coord_map(xlim= c(-180, 180)) +
	labs(title = "Quality of Location")
```

```{r}

renamed_set %>%
	group_by(country) %>%
	ggplot(aes(x = country_iso, y = populationserved)) +
	geom_col()
```

